\documentclass{cv}
\begin{document}
\name{Domagoj Deduš}

Rudeška cesta 168

10000 Zagreb

domagoj.dedus@gmail.com

098 9501 831

Date of birth: 14.1.1992.
\job{JOB APPLIED FOR}{SYSTEM ENGINEER}
\section{EDUCATION AND TRAINING}
\datedsubsection{Electrical Engineer}{2006-2010}
1. tehnička škola Tesla
\datedsubsection{Bachelor of Information Technology}{2010-2014}
The Polytechnic of Zagreb (Tehničko veleučilište u Zagrebu)

Undergraduate professional study programme in Information technologies. e-Business programme.
\datedsubsection{Professional specialist of engineering in Information Technologies}{2015-2017}
College for Information Technologies (VsiTe - Visoka škola za informacijske tehnologije Zagreb)

Graduate professional study of Information technologies. Computer systems programme.
\datedsubsection{Cisco Certified Network Associate Routing and Switching (CCNA Routing and Switching)}{2018-2019}

Cisco ID CSCO13494268
\datedsubsection{SRCE|Sveučilišni računski centar Sveučilišta u Zagrebu}{2019}
\begin{itemize}
    \setlength\itemsep{0.1cm}
    \item Python programming
    \item Advanced Linux System Administration 1
\end{itemize}
\datedsubsection{Oracle Database 12c R2: Administration Workshop Ed3}{2020}

\section{WORK EXPERIENCE}
\datedsubsection{NOC operater (as student) - Optima Telekom d.d.}{02/2016-04/2017}
\begin{itemize}
    \setlength\itemsep{0.1cm}
    \item monitored and and did basic troubleshooting of access, distribution and core ISP network using Zabbix and
Cacti monitoring software
    \item scripted in Bash and Python for monitoring and automatization purposes, for example extracting data from log
files
    \item basic router/switch/DSLAM configuration, was backuping network device configurations using scripts
    \item administrated special purpose Linux application server for multicast traffic monitoring
    \item communicated with other Croatian and international Internet service providers
    \item communicated with field technicians and other IT departments with purpose of resolving issues with
network equipment and other hardware or software
    \item was creating, resolving and forwarding trouble tickets
\end{itemize}
\datedsubsection{System Engineer - Bulb d.o.o.}{04/2017-Ongoing}
\begin{itemize}
    \setlength\itemsep{0.1cm}
    \item Linux systems administration, including email systems (Zimbra, G Suite), backup systems (Bacula), storage systems, monitoring systems (Zabbix, Graphite, Grafana), DHCP and DNS services, LDAP, virtualization and containerization, web servers, load balancers, proxy servers
    \item designing system architectures from hardware, software and networking perspectives
    \item troubleshooting various network and system issues 
    \item administrating database management systems including PostgreSQL, Oracle and MySQL
    \item scripting in Bash, Python and Ansible for the purpose of automatization and monitoring
    \item supporting devops ecosystem applications: Docker, Jenkins, Nexus, gitlab-ci, Sonarqube, Red Hat Openshift
    \item installing and maintaining various middleware servers such as Wildfly and Oracle Weblogic and proprietary java applications
    \item interaction with the clients, attending technical workshops, preparation of documentation
    \item ongoing and proactive education in the segment of system administration and DevOps
    \item mentoring new and existing colleagues in the field of system adminstration
    \item focus on using open source software
\end{itemize}
\section{JOB SKILLS}
Linux (and Windows but in lesser part) system administration, networking, scripting, googling.

Mastery in using Bash shell and general Linux.

Computer forensics, strong emphasis on understanding how "things" work.

Very good in written and spoken English, around C1 level.

B category driving license.

Experience in team leading, orientation on good organization, results and quality of the job done.

Always looking to learn more in the field of Information Technologies - focus is currently on orchestration technologies and completely achieving DevOps way of thinking.
\end{document}
